---
output: 
  md_document:
    variant: markdown_github
---

# WebHDFS

```{r build_coverage_badge_link, echo=FALSE}
coverage_percent <- scan("https://pandafood.mitre.org/browse/CGRP-WEBHDFSM/latest/artifact/JOB1/coverage_percent/coverage_percent.txt", quiet = TRUE)

# colors for:       <30     <50        <70      >70
color_options <- c("red", "orange", "yellow", "green")
color_idx <- findInterval(coverage_percent, c(30,50,70)) + 1
img_path <- paste0("https://img.shields.io/badge/Test%20Coverage-", 
                   coverage_percent, "%25-",   # url encode %25 needed to get %
                   color_options[color_idx],
                   ".svg")

```

[![Bamboo Build Status](https://pandafood.mitre.org/plugins/servlet/wittified/build-status/CGRP-WEBHDFSM)](https://pandafood.mitre.org/browse/CGRP-WEBHDFSM)
[![Test Coverage](`r img_path`)](https://pandafood.mitre.org/artifact/CGRP-WEBHDFSM/JOB1/build-latest/covr_coverage_report/covr_report.html)

Provide an interface to WebHDFS operations by leveraging configuration details from the `clusterconf` package.  This includes functions to facilitate listing directory contents, creating, renaming, or deleting directories.  These common commands have corresponding shortcut functions in this package (e.g. `hdfs_ls`, `hdfs_makedir`, `hdfs_rename`, `hdfs_delete`).

For WebHDFS operations that do not have corresponding functions in this package, it is possible to issue many of those commands through the lower-level functions `hdfs_get` and `hdfs_put`.


## Requirements

This package dynamically builds the URL for WebHDFS services based on cluster settings for namenode, WebHDFS port number, and suffix.  Specifically, the settings `webhdfs.cluster.nn.url`, `webhdfs.cluster.webhdfs.port`, and `webhdfs.cluster.webhdfs.suffix` must be defined.  It is convenient to do this through the `clusterconf` package, although it also possible to set the necessary variables manually through the `set_namenode_url`, `set_webhdfs_port`, and `set_webhdfs_suffix` functions provided in this package.


## Installation

The easiest way is to install the latest stable version from MCRAN. 
Detailed instructions for this are [available](http://mcran.mitre.org/#install-using-install.packages-from-r-preferred) or you can use the snippet below.

```{r, eval=FALSE}
install.packages("webhdfs", 
                 repos=c("https://artifacts.mitre.org/artifactory/cran1-remote",
                         "http://mcran.mitre.org"))
```


## Usage

Here is a simple example to get up and running with this package, where `my cluster name` corresponds to a HDFS cluster whose configuration is defined using the protocol of the `clusterconf` package.

```{r, eval=FALSE}
library(webhdfs)
set_cluster("my cluster name")
hdfs_ls("/data/")
```


