---
output: 
  md_document:
    variant: markdown_github
---

# WebHDFS

Provide an interface to WebHDFS operations by leveraging configuration details from the `clusterconf` package.  This includes functions to facilitate listing directory contents, creating, renaming, or deleting directories.  These common commands have corresponding shortcut functions in this package (e.g. `hdfs_ls`, `hdfs_makedir`, `hdfs_rename`, `hdfs_delete`).

For WebHDFS operations that do not have corresponding functions in this package, it is possible to issue many of those commands through the lower-level functions `hdfs_get` and `hdfs_put`.


## Requirements

This package dynamically builds the URL for WebHDFS services based on cluster settings for namenode, WebHDFS port number, and suffix.  Specifically, the settings `webhdfs.cluster.nn.url`, `webhdfs.cluster.webhdfs.port`, and `webhdfs.cluster.webhdfs.suffix` must be defined.  It is convenient to do this through the `clusterconf` package, although it also possible to set the necessary variables manually through the `set_namenode_url`, `set_webhdfs_port`, and `set_webhdfs_suffix` functions provided in this package.


## Installation

The easiest way is to install the latest development version from GitHub, for example with the `devtools` package. 

```{r, eval=FALSE}
devtools::install_github("mitre/webhdfs")
```


## Usage

Here is a simple example to get up and running with this package, where `my cluster name` corresponds to a HDFS cluster whose configuration is defined using the protocol of the `clusterconf` package.

```{r, eval=FALSE}
library(webhdfs)
set_cluster("my cluster name")
hdfs_ls("/data/")
```


